An Hypernetwork Approach to Accurately Measure Technological Innovation \bigskip\\ \textit{Methods and Results}

### 2015-11-30 Docs/WorkingPapers/methods.tex
kw_export_ok
test_parallel_procesisng

More precisely, let $n = \left|\mathcal{P}\right|$ the number of patents. classes are constructed in $O(n)$ from file giving patents classes, and then sorted in $\Theta (\sum_k{\left|\mathcal{C}_k\right|\cdot \log{\left|\mathcal{C}_k\right|}})$ with $\mathcal{C}_k$ the classes. The number of classes $K$ being fixed, it simplifies into a $O(n\log{n})$.

>>>>

More precisely, let $n = \left|\mathcal{P}\right|$ the number of patents. Classes are constructed in $O(n)$ from file giving patents classes, and then sorted in $\Theta (\sum_k{\left|\mathcal{C}_k\right|\cdot \log{\left|\mathcal{C}_k\right|}})$ with $\mathcal{C}_k$ the classes. The number of classes $K$ being fixed, it simplifies into a $O(n\log{n})$. This sorting allows to compute overlaps and differences between classes in linear time by a direct comparison. To compute higher order overlaps, we have an exponential complexity in the overlap order $o$ (in $O(K^o)$) but order three appears experimentally to have cardinals smaller enough for a reasonable one-to-one technological distance computation. A class partition strategy allows to know any distance : if $o (\mathcal{C}_i,\mathcal{C}_j)$ is first order overlap between classes $i$ and $j$ and $o_2 (\mathcal{C}_i,\mathcal{C}_j,\mathcal{C}_k)$ second order overlap (i.e. $o(\mathcal{C}_k,o(\mathcal{C}_i,\mathcal{C}_j))$, then for any class $i$,
\begin{itemize}
\item between any $p\in \mathcal{C}_i \\ \cup_{k}{o(i,k)}$, proximity is necessarily 1 (one class in common for one-class patents)
\item for any $j \neq i$
\end{itemize}
